Notes

### 2023-12-21 chapters/appendix-code.tex
Add experiments folder to appendix on source code

\begin{itemize}
  \item In the \texttt{rkbfr} folder we find the files responsible for the implementation of our models, separated according to the functionality they provide.
  \item The \texttt{reference\_methods} folder contains our implementation of the functional comparison algorithms that were not available through a standard Python library.
  \item The \texttt{utils} folder contains some utility files for simulation, experimentation and visualization.
  \item At the root folder we have files for executing our experiments, which accept many user-specified parameters (e.g. number of iterations, type of data set, \ldots). In particular, the script \texttt{results\_cv.py} contains the code for our comparison experiments, while the script \texttt{results\_all.py} allows the execution of our Bayesian methods without a cross-validation loop.
\end{itemize}

>>>>

\begin{itemize}
  \item In the \texttt{rkbfr} folder we find the files responsible for the implementation of our Bayesian models, separated according to the functionality they provide.
  \item The \texttt{reference\_methods} folder contains our implementation of the functional comparison algorithms that were not available through a standard Python library.
  \item The \texttt{utils} folder has some utility files for simulation, experimentation and visualization.
  \item The \texttt{experiments} folder contains plain text files with the numerical experimental results shown in Appendix~\ref{ch:tables}, as well as \texttt{.csv} and \texttt{.npz} files that facilitate working with them directly in Python.
  \item At the root folder we have files for executing our experiments, which accept several user-specified parameters (such as the number of iterations or the type of data set). In particular, the script \texttt{results\_cv.py} contains the code for our comparison experiments, while the script \texttt{results\_all.py} executes our Bayesian methods without a cross-validation loop.
\end{itemize}
